Implementation and Analysis of Homomorphic Facial Image Encryption and Manipulation

### 2019-03-17 icmssp-paper/parts/03_methodology.tex
Shortening Ch2-3

\section{Methodology}
\label{sec:chapter_3}
We apply three homomorphic encryption schemes~\cite{ziad_cryptoimg:_2016, pieprzyk_efficient_2007, garay_algorithms_2014} for use in image processing and facial recognition applications. In particular, the study consists of the following:
\begin{itemize}
	\item Creating a wrapper library that acts as a unified interface which implements the Paillier, DGK, and BGV homomorphic cryptosystems.
	\item An implementation of image processing operations (intensity transformations, facial recognition) under the above cryptosystems.
	\item Conducting tests for image quality, processing time, using images from the \texttt{faces94} dataset.
\end{itemize}

@@

\subsection{Cryptosystem Implementation}
Three homomorphic encryption schemes are investigated, and a wrapper library was created in Python that integrates these cryptosystems into a unified interface.
\begin{itemize}
	\item The Paillier cryptosystem is incorporated using the python-paillier library at \url{https://github.com/n1analytics/python-paillier} developed by Data61 - CSIRO.
	\item The DGK cryptosystem is ported from the C++ implementation at \url{https://github.com/encryptogroup/ENCRYPTO_utils}, developed by Daniel Demmler from EC-SPRIDE.
	\item The BGV cryptosystem is implemented using the Pyfhel library (\url{https://github.com/ibarrond/Pyfhel}) using a HElib backend from (\url{https://github.com/shaih/HElib}).
\end{itemize}

\subsubsection{Extension of Partially Homomorphic Cryptosystems}
\label{sssec:pheextension}
In order to use Paillier and DGK for secure image processing, we require the two schemes to support the encryption of floating-point (FP) numbers, as well as multiplication and division of arbitrary ciphertexts. We extend the two cryptosystems to FP operations by using an approach shown in~\cite{ziad_cryptoimg:_2016}. This approach represents FP numbers using a pair $(m,e)$, where $m$ represents the mantissa (which is encrypted), and $e$ represents the exponent (which is not encrypted). This approach is also used by the python-paillier library. This represntation allows us to extend the addition and plaintext multiplication homomorphisms of the Paillier and DGK cryptosystems to floating-point numbers.

Various two-party protocols can be used to facilitate ciphertext multiplication and division. These allow a server armed with only knowledge of the public key, to obtain the product and quotient of ciphertexts, by communicating with the client, who has the private key. For division, we use the protocol defined in~\cite{boukoros_lightweight_2017}: to obtain $E(x/y)$ from $E(x)$ and $E(y)$, the server sends $E(rx)$ and $E(ry)$ to the client, (where $r$ is a random non-zero number), allowing the client to compute $E(rx/ry)$ and give the result back to the server.

For multiplication, we adapt the protocol to calculate Euclidean distances used in \cite{hutchison_privacy-preserving_2009}, which provides a two-party protocol which yields $E(x^2)$ given $E(x)$. We use this protocol together with the additive homomorphism of the partially homomorphic cryptosystems to instead compute $E((x + y)^2 - x^2 - y^2) = E(2xy)$, from which we can easily obtain $E(xy)$ through plaintext multiplication.

@@

The benchmarks to be used in the study, adopted from~\cite{ahmed_benchmark_2016, ahmad_efficiency_2012, wu_npcr_2011} are listed below. We let $X_i$ denote a value in an image $X$, where $1 \leq i \leq N$.
We first perform three tests to ascertain the preservation of image quality after encryption and decryption: MSE, PSNR, and SSIM.
\begin{description}
	\item [Mean Squared Error (MSE).] The MSE is defined in~\cite{ahmed_benchmark_2016} as
	\begin{align}
        \mathrm{MSE} = \frac{1}{N}\sum_{i=1}^{N}{(\mathrm{CDT}_i - \mathrm{PDT}_i)^2}.
	\end{align}
	The MSE provides a measure of how much data is recovered if an image operation is applied on the encrypted image, which is then decrypted. Lower values of MSE indicate higher preservation of image quality~\cite{ahmed_benchmark_2016, ahmad_efficiency_2012}.
	\item [Peak Signal to Noise Ratio (PSNR).]
	According to Ahmed, et al.~\cite{ahmed_benchmark_2016}, PSNR is ``an estimator for human visual perception of reconstruction quality.'' It has been used to ascertain image quality in various studies and is a known metric for image and video quality~\cite{upmanyu_efficient_2009, jain_image_2016, akramullah_video_2014}. Although it may produce results which do not correlate with human visual perception~\cite{huynh-thu_accuracy_2012, ahmed_benchmark_2016}, it is a valid indicator of image quality when media containing the same visual content is compared~\cite{huynh-thu_accuracy_2012}.
	PSNR is defined by
	\begin{align}
        \mathrm{PSNR} = 10\log_{10}{\left( \frac{L^2}{\mathrm{MSE}} \right)}
	\end{align}
	where $L$ is the maximum pixel intensity value of an image.
	Despite the known limitations of PSNR, since we are going to compare the effect of each encryption scheme on recovered image quality, given a fixed library of images, it is a valid measure of image quality for the study. A higher PSNR indicates higher image quality preservation.
	\item [Structural Similarity Index (SSIM).]
	The SSIM for two random variables $X$ and $Y$ is defined in~\cite{ahmed_benchmark_2016, akramullah_video_2014} as
	\begin{align}
        \mathrm{SSIM}(X,Y) = \frac{(2\mu_X\mu_Y+c_1)(2\sigma_{XY}+c_2)}{(\mu_X^2+\mu_Y^2+c_1)(\mu_X^2+\mu_Y^2+c_2)}
	\end{align}
	where
	\begin{itemize}
		\item $\mu_X, \mu_Y$ are the averages of $X$ and $Y$, respectively;
		\item $\sigma_X, \sigma_Y$ are the variances of $X$ and $Y$, respectively;
		\item $\sigma_{XY}$ is the covariance of $X$ and $Y$;
		\item $c_1 = (k_1L)^2, c_2 = (k_2L)^2$ are two variables used to stabilize the measure when $\mu_X^2+\mu_Y^2$ is close to zero~\cite{akramullah_video_2014};
		\item $L$ is the the maximum pixel intensity value of an image;
		\item $k_1 = 0.01, k_2 = 0.03$ by default, given in~\cite{ahmed_benchmark_2016}.
	\end{itemize}
	The SSIM is applied to the luminance value of two images to gauge structural similarity between neighboring pixels.
	For the study, we computed $\mathrm{SSIM}(\mathrm{PDT}, \mathrm{CDT})$ for every image operation, under each homomorphic cryptosystem. Higher values of SSIM indicate higher structural similarity, and an SSIM of $1$ indicates that the two images are identical~\cite{ahmed_benchmark_2016}.
\end{description}

>>>>

\section{Methodology}
\label{sec:chapter_3}
% We apply three homomorphic encryption schemes~\cite{ziad_cryptoimg:_2016, pieprzyk_efficient_2007, garay_algorithms_2014} for use in image processing and facial recognition applications. In particular, the study consists of the following:
% \begin{itemize}
% 	\item Creating a wrapper library that acts as a unified interface which implements the Paillier, DGK, and BGV homomorphic cryptosystems.
% 	\item An implementation of image processing operations (intensity transformations, facial recognition) under the above cryptosystems.
% 	\item Conducting tests for image quality, processing time, using images from the \texttt{faces94} dataset.
% \end{itemize}

@@

\subsection{Cryptosystem Implementation}
A wrapper library was created in Python that integrates the Paillier, DGK, and BGV cryptosystems into a unified interface.
\begin{itemize}
	\item The Paillier cryptosystem is incorporated using the python-paillier library at \url{https://github.com/n1analytics/python-paillier} developed by Data61 - CSIRO.
	\item The DGK cryptosystem is ported from the C++ implementation at \url{https://github.com/encryptogroup/ENCRYPTO_utils}, developed by Daniel Demmler from EC-SPRIDE.
	\item The BGV cryptosystem is implemented using the Pyfhel library (\url{https://github.com/ibarrond/Pyfhel}) using a HElib backend from (\url{https://github.com/shaih/HElib}).
\end{itemize}

@@

The benchmarks to be used in the study, adopted from~\cite{ahmed_benchmark_2016, ahmad_efficiency_2012, wu_npcr_2011} are listed below. We let $X_i$ denote a value in an image $X$, where $1 \leq i \leq N$.
We first perform three tests to ascertain the preservation of image quality after encryption and decryption: MSE, PSNR, and SSIM.
\begin{description}
	\item [Mean Squared Error (MSE).] The MSE is defined in~\cite{ahmed_benchmark_2016} as
	\begin{align}
        \mathrm{MSE} = \frac{1}{N}\sum_{i=1}^{N}{(\mathrm{CDT}_i - \mathrm{PDT}_i)^2}.
	\end{align}
	The MSE provides a measure of how much data is recovered if an image operation is applied on the encrypted image, which is then decrypted. Lower values of MSE indicate higher preservation of image quality~\cite{ahmed_benchmark_2016, ahmad_efficiency_2012}.
	\item [Peak Signal to Noise Ratio (PSNR).]
	The PSNR is ``an estimator for human visual perception of reconstruction quality.''~\cite{ahmed_benchmark_2016}. Although it may produce results which do not correlate with human visual perception~\cite{huynh-thu_accuracy_2012, ahmed_benchmark_2016}, it is a valid indicator of image quality when media containing the same visual content is compared~\cite{huynh-thu_accuracy_2012}, and is a known metric for image and video quality~\cite{upmanyu_efficient_2009, jain_image_2016, akramullah_video_2014}.
	PSNR is defined by
	\begin{align}
        \mathrm{PSNR} = 10\log_{10}{\left( \frac{L^2}{\mathrm{MSE}} \right)}
	\end{align}
	where $L$ is the maximum pixel intensity value of an image. A higher PSNR indicates higher image quality preservation.
	\item [Structural Similarity Index (SSIM).]
	The SSIM for two random variables $X$ and $Y$ is defined in~\cite{ahmed_benchmark_2016, akramullah_video_2014} as
	\begin{align}
        \mathrm{SSIM}(X,Y) = \frac{(2\mu_X\mu_Y+c_1)(2\sigma_{XY}+c_2)}{(\mu_X^2+\mu_Y^2+c_1)(\mu_X^2+\mu_Y^2+c_2)}
	\end{align}
	where
	\begin{itemize}
		\item $\mu_X, \mu_Y$ are the averages of $X$ and $Y$, respectively;
		\item $\sigma_X, \sigma_Y$ are the variances of $X$ and $Y$, respectively;
		\item $\sigma_{XY}$ is the covariance of $X$ and $Y$;
		\item $c_1 = (k_1L)^2, c_2 = (k_2L)^2$ are two variables used to stabilize the measure when $\mu_X^2+\mu_Y^2$ is close to zero~\cite{akramullah_video_2014};
		\item $L$ is the the maximum pixel intensity value of an image;
		\item $k_1 = 0.01, k_2 = 0.03$ by default, given in~\cite{ahmed_benchmark_2016}.
	\end{itemize}
	The SSIM is applied to the luminance value of two images to gauge structural similarity between neighboring pixels.
	For the study, we computed $\mathrm{SSIM}(\mathrm{PDT}, \mathrm{CDT})$ for every image operation, under each homomorphic cryptosystem. Higher values of SSIM indicate higher structural similarity, and an SSIM of $1$ indicates that the two images are identical~\cite{ahmed_benchmark_2016}.
\end{description}
